%Feel free to replace the manual listing below with something else, e.g. using the nomencl or glossaries package


\chapter{Nomenclature}
\label{chapter:nomencl}

\emph{This could a place to show off some graph-related mathematical notations. Removing the chapter is a more likely option, however.}

In 2006, Jyri Engeström and Petteri Koponen founded Jaiku, a social media before social media. Next year, Google acquired Jaiku and Engeström and Koponen moved forward, first to work at Google and then to other startup and business ventures. Currently, Koponen is one of the founders of Lifeline Ventures, a venture capital investment company. Lifeline Venture's portfolio includes Supercell, a game-development company that, in 2015, is one of the keystone companies of the Finnish Innovation Ecosystem. In 2014, Supercell CEO Ilkka Paananen and Petteri Koponen after a Japanese giant acquired part of Supercell, Supercell CEO and Koponen together with the Timo Ahopelto, also a partner at Lifeline Ventures, joined to start up a new fund\footnote{Supercell-miljonäärit ryhtyvät sijoittajiksi, \url{http://www.hs.fi/talous/a1398050554829}} for providing seed level funding to Finnish Startups and growth companies.

After receiving information on just a few of these kinds of storylines or chains of action, as humans with limited cognition, we begin to loose the big picture, the system-level view. Is there a way to represent these stories in data and to quantify them for analysis and visualization?

The thesis of this dissertation is that visual network analytics is an imperative approach in allowing the exploration of innovation ecosystem structure. A graph is composed of nodes and edges connecting the nodes.

… 

% DO NOT START WRITING A SECTION ON GRAPH AND NETWORK BASICS BEFORE SOMEONE ACTUALLY INSISTS ON DOING SO! :)

% \textbf{Latin alphabet}
% \begin{longtable}[l]{p{2cm} p{12cm} }
% $^{i}a^{x}_{P_{\,i}^j}$ & $x$ axis component of $^i\mathbf{a}_{P_{\,i}^j}$    \\
% $\{B\}$ & body coordinate frame  \\
% $\mathbf{\dot{x}}^{\,ref}$ & end-effector velocity reference  \\
% $Y(s)$ & position output \\
% \end{longtable}

% \textbf{Greek alphabet}
% \begin{longtable}[l]{p{2cm} p{12cm}}
% $_G\,\boldsymbol{\alpha}_B$ & angular acceleration of $\{B\}$ with respect to $\{G\}$ \\
% $^{i}\boldsymbol{\alpha}_i$ & angular velocity of $\{B_i\}$ with respect to $\{I\}$ expressed in $\{B_i\}$  \\
% $\boldsymbol{\mu}_m$ & additive magnetometer measurement noise \\
% $^i_j\,\boldsymbol{\dot{\omega}}_{k}$ & angular acceleration of $\{B_{k}\}$ relative to $\{B_j\}$ expressed in $\{B_i\}$  \\
% \end{longtable}
