\chapter{List of Publications}

\begin{midsloppypar}

This dissertation is a compilation of seven (7) publications, of which four (2) are journal articles, four (4) appear in conference proceedings and one (1) is published as a chapter of a peer-reviewed scientific book.

In this section, we will describe the role of the author of this dissertation in each of the publications and add further information about them. Finnish Publication Forum\footnote{Finnish Publication Forum, \url{http://www.tsv.fi/julkaisufoorumi/english.php}} ratings are used to roughly indicate the quality of the publication channels. Level 3 is the highest.

\begin{enumerate}[label=\textbf{Publication \Roman*},align=left]

  \item Jukka Huhtamäki, Ville Luotonen, Ville Kairamo, Kaisa Still, Martha G. Russell 
  (2013)
  ``Process for Measuring and Visualizing an Open Innovation Platform: Case Demola,''
  \emph{Academic MindTrek 2013, Tampere, Finland}.
  Publication Forum level 1.
  \label{pub:demola}

  \item Rahul C. Basole, Martha G. Russel, Jukka Huhtamäki, Neil Rubens
  (2012)
  ``Understanding Mobile Ecosystem Dynamics: A Data-Driven Approach,''
  \emph{International Conference on Mobile Business (ICMB)}.
  Publication Forum level 1.
  \label{pub:mobileecosystem}

  \item Jukka Huhtamäki, Kaisa Still, Minna Isomursu, Martha G. Russell and Neil Rubens
  (2012)
  ``Networks of Growth: The Case of Young Innovative Companies in Finland,'' 
  \emph{The 7th European Conference on Entrepreneurship and Innovation (ECIE 2012), Santarém, Portugal}.
  Publication Forum level 0.
  \label{pub:tekesyic}

  \item Jukka Huhtamäki, Martha G. Russell, Kaisa Still, Neil Rubens
  (2013)
  ``A Network-Centric Snapshot of Value Co-Creation in Finnish Innovation Financing,'' 
  \emph{Value Co-Creation: Best of TIM Review}.
  Publication Forum level 0; TIM Review was promoted to Publication Forum level 1 in 2015.
  \label{pub:finland}

  \item Kaisa Still, Jukka Huhtamäki, Martha G. Russell, Rahul C. Basole, Jaakko Salonen, Neil Rubens
  (2013)
  ``Networks of innovation relationships: multiscopic views on Finland,''
  \emph{International Society for Professional Innovation Management (ISPIM) 2013, Helsinki}.
  Publication Forum level 0.
  \label{pub:multiscopicfinland}

  \item Kaisa Still, Jukka Huhtamäki, Martha G. Russell, Neil Rubens
  (2014)
  ``Insights for orchestrating innovation ecosystems: the case of EIT ICT Labs and data-driven network visualisations,''
  \emph{International Journal of Technology Management}.
  Publication Forum level 1. 
  \label{pub:eitictlabs}
  
  \item Jukka Huhtamäki, Martha G. Russell, Neil Rubens, Kaisa Still 
  (2015) 	
  ``Ostinato: The exploration-automation cycle of user-centric, process-automated data-driven visual network analytics,'' in Sorin Adam Matei,
Elisa Bertino, Russell, Martha G. (Eds.) \emph{Transparency in Social Media: Tools, Methods and Algorithms for Mediating Online Interactions},
  Springer. Publication Forum level 2.
  \label{pub:ostinato}
  
\end{enumerate}

\section{Authors role and quality of publication channels}

The series of investigations that form the first part of results for this dissertation are conducted by the Innovation Ecosystems Network (IEN) team. The majority of the work took place under Tekes innovation research projects SINDI (2010-2012), REINO (2012-2015) and SPEED (2014-2016). The author of this dissertation is one of the co-founders of IEN. Martha G. Russell, mediaX at Stanford University, leads the IEN team that include Kaisa Still, VTT Technical Research Centre of Finland  Ltd; Neil Rubens, University of Electro-Communications, Tokyo; Rahul C. Basole, Georgia Tech and Camilla Yu, VXPLO Innovation Lab.

The author of the dissertation has led the design, development and operation of the data-driven visual analytics process in each of the investigations. Moreover, the author has written the majority of the manuscript for \ref{pub:demola}, \ref{pub:tekesyic}, \ref{pub:finland} and \ref{pub:ostinato}. In others, the author has made significant contributions to research design, manuscripts, analysis, discussion, and research project management.

\ref{pub:demola} was presented by the author of this dissertation at Academic MindTrek in Tampere, Finland. Academic MindTrek (MindTrek Conference in Publication Forum) is placed in Publication Forum level 1.

\ref{pub:mobileecosystem} received the Best Paper Award in International Conference on Mobile Business (ICMB). Rahul Basole gave the presentation. Extended version of the paper was later published in \emph{ACM Transactions on Management Information Systems} (ACM TMIS). ICMB is in Publication Forum level 1.

\ref{pub:tekesyic} was presented by the author of this dissertation at ECIE 2012 in Santarém, Portugal. ECIE is placed in Publication Forum level 0.

\ref{pub:finland} was originally presented by the author of this dissertation at the 10th annual EBRF conference in Nokia, Finland. The article was first invited to \emph{Technology Innovation Management Review} and later selected to be included into a Best of TIM Review book on co-creation. In 2015, TIM Review was promoted to Publication Forum level 1.

\ref{pub:multiscopicfinland} was co-presented by Kaisa Still and the author of this dissertation at ISPIM in Helsinki. While ISPIM is placed in Publication Forum level 0, it is considered a key yearly meeting in innovation research domain.

\ref{pub:eitictlabs} was invited to be published in a Special Issue of International Journal of Technology Management (IJTM) on Business and Network Models for Innovation. IJTM is placed in Publication Forum level 1.

\ref{pub:ostinato} was selected to be included in the second volume of Roles, Trust, and Reputation in Social Media Knowledge Markets, a book published by Springer. As a book publisher, Springer is placed in Publication Forum level 2.

\end{midsloppypar}